Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-13 paper/paper.qmd
Finished reviewing survey and updated intro and data section

For the remainder of the paper, the data section (@sec-data) goes over the data we used and its features and limitations, how the dataset was obtained, our variables of interest for our model and preliminary analysis, and a bit of our data cleaning process. In the model section (@sec-model), it discusses the type of model we used, the relationships between variables in our model, and the justification for our model. The results section (@sec-results) contains tables and graphs created based on our data and the results from our model. In the discussion section (@sec-discussion), it goes over what we did in our results, explaining the meaning of our findings, the implications of our findings to the real world, and areas of improvement and suggestions for future works. In the appendix (@sec-appendix), it includes a link to the dashboard that includes interactive versions of the graphs in this paper, additional tables, notes on reproducing and code styling, model diagnostics and validation, and our idealized survey and methodology to gather more data on investigators responsible for homicide cases.

@@

The raw dataset we retrieved from The Washington Post using a script that downloads the CSV file from their GitHub repository contains 52,179 observations with one observation being a homicide case. However, since we narrowed our scope to focus on the two of the most populated US cities, Los Angeles and Chicago, the number of observations in our cleaned dataset ended up being 6,307. Our data look as follows:

@@

### Idealized Survey Design
We will create our survey using Google Form since it is the survey platforn people are the most familiar with in terms of the user interface. When designing our survey we also considered different respondent biases that could occur. For example, response order bias occurs when respondents choose answers based on their order [@citeStantcheva]. To address this bias, for questions with ordinal scales we will be reversing the ordering at random [@citeStantcheva]. Another bias that could occur is social desirability bias, in which respondents would pick an answer in order to be perceived positively by others [@citeStantcheva]. To address this bias, we will reassure respondents in the survey that their response will not be shared with other members on their team and their response will be only seen by the research team and that they can choose to contact us and withdraw their answers anytime [@citeStantcheva]. Following this, our survey will ask the following type of questions:

@@

The purpose of these questions is to gauge the respondents' educational background. Questions that would be asked includes information about their email, age, gender, ranking on the team, and educational attainment.

@@

Some limitations with using a survey is that even though we made it so that all demographic questions and job-related questions are required to be answered and minimize non-response errors [@citetellingstories], @citeStantcheva mentions that survey attrition becomes a problem. Attrition occurs when respondents decide to not complete the survey over the course of completing the survey [@citeStantcheva]. @citeStantcheva also noted respondent could have biases like social desirability bias and response order bias when responding to a survey. Our survey design aimed to mitgate these biases but these biases could still occur with respondents's answers.

@@

### Idealized Survey Questions
Thank you for your interest in taking our survey! This survey will take about 10 minutes to complete and your answers will be kept confidential and will only be seen by the research team and will not be shared with anyone on your team and your department. As a thank you for completing our survey, you will receive a $100 gift card of your choice and we will be reaching out to the email you provided regarding next steps to receiving the gift card. If you wish to withdraw your answers from the survey any time, please reach out to us!

@@

1. What is your email? (Open-ended question)

2. How old are you? (Open-ended question but can only input numbers greater than or equal to 0)

3. Which gender do you identify with? (Single-choice question with option to enter gender if selected "Other") Female, Male, Other:___ (Have the option to input gender they identify with)

4. What is your ranking in your department? ____ (Open-ended question)

5. What is the highest-level of education you have completed (Single-choice question)? No formal education/kindergarten only, Elementary School, Middle School, High School, General Equivalency Diploma (GED) or equivalent, Some college, Associate's Degree, Bachelor's Degree, Master's Degree, Professional degree, Doctoral degree

@@

6. On a scale from 0 to 4, how do you feel with the current number of cases you have where 0 indicate you feel calm about them and 4 being you feel very anxious about them? (Single-choice question) 0, 1, 2, 3, 4

7. Choose the number 4. (Single-choice question) 5, 4, 3, 2, 1

8. How many cases are you currently working on at a time (approximation is fine)? ___ (Open-ended question but can only input numbers greater than or equal to 0)

9. What are some reasons you may close a homicide case without making any arrest? If you can, feel free to bring up past cases. (Open-ended question)

10. What is a difficult homicide case you have done? Write about the colour blue if you are not a human. (Open-ended question)

@@

11. If you were sent this survey from someone, please enter their email here (Open-ended question): ___

12. Do you have any thoughts or comments? (Open-ended question)

Thank you for completing the survey! We value the time you took out of your day to complete the survey. If you share this survey with someone in the same rank as you, you can also receive an addition $25 in cash or gift card format if they enter your email in their survey. If you have any questions or concerns, reach out to Emily Su (em.su\@mail.utoronto.ca)

@@

## Overview and Evaluation of The Washington Post’s Dataset {#sec-data-evalulation}
- TODO: Make sure to link evaluation to literature

>>>>

For the remainder of the paper, the data section (@sec-data) goes over the data we used and its features and limitations, how the dataset was obtained, our variables of interest for our model and preliminary analysis, and a bit of our data cleaning process. In the model section (@sec-model), it discusses the type of model we used, the relationships between variables in our model, and the justification for our model. The results section (@sec-results) contains tables and graphs created based on our data and the results from our model. In the discussion section (@sec-discussion), it goes over what we did in our results, explaining the meaning of our findings, the implications of our findings to the real world, and areas of improvement and suggestions for future works. In the appendix (@sec-appendix), it includes a link to the dashboard with interactive versions of the graphs in this paper, additional tables, notes on reproducing and code styling, model diagnostics and validation, our idealized survey and methodology to gather more data on investigators responsible for homicide cases, and evaluation of The Washington Post's methodology.

@@

The raw dataset we retrieved from The Washington Post using a script that downloads the CSV file from their GitHub repository contains 52,179 observations with each observation being a homicide case. However, since we narrowed our scope to focus on the two of the most populated US cities, Los Angeles and Chicago, the number of observations in our cleaned dataset ended up being 6,307. Our data look as follows:

@@

### Idealized Survey Design
We will create our survey using Google Form since it is the survey platform people are the most familiar with in terms of the user interface. When designing our survey we considered different respondent biases that could occur. For example, response order bias occurs when respondents choose answers based on their order [@citeStantcheva]. To address this bias, for questions with ordinal scales we will be reversing the ordering at random [@citeStantcheva]. Another bias that could occur is social desirability bias, in which respondents would pick an answer in order to be perceived positively by others [@citeStantcheva]. To address this bias, we will reassure respondents in the survey that their response will not be shared with other members on their team and will be only seen by the research team  [@citeStantcheva]. Respondents can also choose to contact us and withdraw their answers anytime and during our data analysis, emails will be omitted to anonymize individuals. Following this, our survey will ask the following type of questions:

@@

The purpose of these questions is to gauge the respondents' personal background. Questions that would be asked includes their email and information about their age, gender, ranking on the team, and educational attainment.

@@

Some limitations with using a survey is that even though we designed it so that answers are required for all demographic questions and job-related questions and therefore minimize non-response errors [@citetellingstories], @citeStantcheva mentions that survey attrition becomes a problem. Attrition occurs when respondents decide to not complete the survey over the course of completing the survey [@citeStantcheva]. @citeStantcheva also noted respondent could have biases like social desirability bias and response order bias when responding to a survey. Our survey design aimed to mitigate these biases but they could still occur with respondents's answers.

@@

### Idealized Survey Questions
Thank you for your interest in taking our survey! This survey will take about 10 minutes to complete. Your answers will be kept confidential and only be seen by the research team and not be shared with your department. Your work email will be used for verification purposes however we will be omitting your email during our analysis to anonymize your responses. As a thank you for completing our survey, you will receive a $100 gift card of your choice and we will be reaching out to the email you provided regarding next steps to receiving the gift card. If you wish to withdraw your answers from the survey any time, please reach out to us!

@@

1. What is your work email? This is used for verification purposes. (Open-ended question)

2. Which gender do you identify with? (Single-choice question with option to enter gender if selected "Other") Female, Male, Other:___ (Have the option to input gender they identify with)

3. What is your ranking in your department? ____ (Open-ended question)

4. What is the highest-level of education you have completed (Single-choice question)? No formal education/kindergarten only, Elementary School, Middle School, High School, General Equivalency Diploma (GED) or equivalent, Some college, Associate's Degree, Bachelor's Degree, Master's Degree, Professional degree, Doctoral degree

@@

5. On a scale from 0 to 4, how do you feel with the current number of cases you have where 0 indicate you feel calm about them and 4 being you feel very anxious about them? (Single-choice question) 0, 1, 2, 3, 4

6. Choose the number 4. (Single-choice question) 5, 4, 3, 2, 1

7. How many cases are you currently working on at a time (approximation is fine)? ___ (Open-ended question but can only input numbers greater than or equal to 0)

8. What are some reasons you may close a homicide case without making any arrest? Feel free to mention past cases you have done in your answer. (Open-ended question)

9. What is a difficult homicide case you have done? Write about the colour blue if you are not a human. (Open-ended question)

@@

10. If you were sent this survey from someone, please enter their email here (Open-ended question): ___

11. Do you have any thoughts or comments? (Open-ended question)

Thank you for completing the survey! We value the time you took out of your day to complete the survey. If you share this survey with someone in the same rank as you, you can receive an addition $25 in cash or gift card format if they enter your email in their survey. If you have any questions or concerns, reach out to Emily Su (em.su\@mail.utoronto.ca)

@@

## Overview and Evaluation of The Washington Post’s Methodology {#sec-data-evalulation}
- TODO: Make sure to link evaluation to literature
